\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-20 bare_conf.tex
Added missing packages.
fixes according to review remarks.

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt,conference,compsocconf]{IEEEtran}
%\documentclass[10pt]{IEEEtran}
\usepackage{times}
\usepackage{color}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{etoolbox}
\usepackage[dvipsnames]{xcolor}

@@

%%%%\IEEEauthorrefmark{2}andrius.budrionis@vgtu.lt,
%%%%\IEEEauthorrefmark{3}audrius.indriulionis@vgtu.lt,
%%%\\\IEEEauthorrefmark{4}darius.plikynas@vgtu.lt}}
% second version of affilation
\author[1]{Povilas Daniu\v{s} Darius Plikynas}
\author[1,2]{Andrius Budrionis}
\author[1,3]{ Audrius Indriulionis}
\affil[1]{Department of Business Technologies  and Entrepreneurship 
\authorcr Gediminas Technical University 
\authorcr Vilnius, Lithuania
\authorcr Email: {\tt \{povilas.daniusis, darius.plikynas\}@vgtu.lt}\vspace{1.5ex}}
\affil[2]{Norwegian Centre for E-health Research 
\authorcr University Hospital of North Norway
\authorcr Troms\o, Norway
 \authorcr Email: {\tt andrius.budrionis@ehealthresearch.no} \vspace{1.5ex}} 
\affil[3]{Laboratory of Quaternary Research 
\authorcr  Nature Research Centre
\authorcr Vilnius, Lithuania
\authorcr Email: {\tt audrius.indriulionis@gmail.com}}

@@

However, some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel. For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description. More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{: for example, adsd .} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.

@@

\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M. Smart Assistive Navigation System for Blind and Visually Impaired Individuals. 2015 International Conference on Advances in Biomedical Engineering (ICABME), 2015.

\bibitem{Dunai} Dunai, L. D., Lengua, I. L., Tortajada, I., Brusola Simon, F. Obstacle detectors for visually impaired people. 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM), 2014.

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt,conference,compsocconf]{IEEEtran}
%\documentclass[10pt]{IEEEtran}
\usepackage{times}
\usepackage{color}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{etoolbox}
\usepackage[dvipsnames]{xcolor}
\usepackage{authblk}
\usepackage{blindtext}

@@

%%%%\IEEEauthorrefmark{2}andrius.budrionis@vgtu.lt,
%%%%\IEEEauthorrefmark{3}audrius.indriulionis@vgtu.lt,
%%%\\\IEEEauthorrefmark{4}darius.plikynas@vgtu.lt}}
% second version of affilation
\author[1]{Povilas Daniu\v{s}is}
\author[1,2]{Andrius Budrionis}
\author[1,3]{ Audrius Indriulionis}
\author[1]{ Darius Plikynas}
\affil[1]{Department of Business Technologies  and Entrepreneurship 
\authorcr Gediminas Technical University 
\authorcr Vilnius, Lithuania
\authorcr Email: {\tt \{povilas.daniusis, darius.plikynas\}@vgtu.lt}\vspace{1.5ex}}
\affil[2]{Norwegian Centre for E-health Research 
\authorcr University Hospital of North Norway
\authorcr Troms\o, Norway
 \authorcr Email: {\tt andrius.budrionis@ehealthresearch.no} \vspace{1.5ex}} 
\affil[3]{Laboratory of Quaternary Research 
\authorcr  Nature Research Centre
\authorcr Vilnius, Lithuania
\authorcr Email: {\tt audrius.indriulionis@gmail.com}}

@@

However, some types of guidance information may be more efficiently perceived through tactile feedback device than audio channel. For instance, indicating the direction of a detected object with a vibromotor on the corresponding area on the forehead belt, instead of providing audio description. More research is needed to clarity how various types of guidance information should be represented to the user in the most convenient and efficient way \textcolor{red}{(e.g. presentation order of object detections may be configured by the system's user according to subjective importance of particular object classes or other personalized criteria).} USB and Wifi data links can be used for bidirectional data transmission between UI and smartphone component.

@@

\bibitem{Owayjan} Owayjan, M., Hayek, A., Nassrallah, H., Eldor, M. Smart Assistive Navigation System for Blind and Visually Impaired Individuals. 2015 International Conference on Advances in Biomedical Engineering (ICABME), pp. 162-165, 2015.

\bibitem{Dunai} Dunai, L. D., Lengua, I. L., Tortajada, I., Brusola Simon, F. Obstacle detectors for visually impaired people. 2014 International Conference on Optimization of Electrical and Electronic Equipment (OPTIM),  pp. 809-816, 2014.
